HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-30 paper/main.tex
typos
Added authors and changed styles for upload to Arxiv

\documentclass[11pt,letterpaper]{article}
%\usepackage[round]{natbib}
\usepackage{emnlp2016}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{url}
\usepackage{pgfplotstable}
\usepackage{titlesec}
%\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum,adjustbox}
\usepackage[font={small}]{caption}

@@

@@

\author{Author 1\\
	    XYZ Company\\
	    111 Anywhere Street\\
	    Mytown, NY 10000, USA\\
	    {\tt author1@xyz.org}
	  \And
	Author 2\\
  	ABC University\\
  	900 Main Street\\
  	Ourcity, PQ, Canada A1A 1T2\\
  {\tt author2@abc.ca}}

@@

Human evaluation of machine translation normally uses sentence-level measures such as relative ranking or adequacy scales. However these provide no insight into possible errors,
and do not scale well with sentence length.
We argue for a semantics-based evaluation, which captures what meaning components
are retained in the MT output, providing a more fine-grained analysis of
translation quality, and enables the construction and tuning of semantics-based MT. 
We present a novel human semantic evaluation measure, Human
UCCA-based MT Evaluation (HUME), building on the UCCA semantic representation scheme.
%Making progress over previous work, the proposed measure takes into account
HUME covers
a wider range of semantic phenomena than previous methods and does not rely on semantic annotation
of the potentially garbled MT output. 
%itself, whose interpretation is often unclear.
We experiment with four language pairs, demonstrating HUME's broad applicability,
and report good
%as well as its reliability, reflected in its 
inter-annotator agreement rates and 
 correlation with human adequacy scores.

>>>>

\documentclass[11pt,letterpaper]{article}
%\usepackage[round]{natbib}
\usepackage{acl2016}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{url}
\usepackage{pgfplotstable}
\usepackage{titlesec}
%\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum,adjustbox}
\usepackage[font={small}]{caption}
\aclfinalcopy

@@

\newcommand*{\affaddr}[1]{#1} 
\newcommand*{\affmark}[1][*]{\textsuperscript{#1}}
\newcommand*{\email}[1]{\texttt{#1}}

@@

\author{
Alexandra Birch\textsuperscript{1}, Barry Haddow\textsuperscript{1}, Ond{\v{r}}ej Bojar\textsuperscript{2}, Omri Abend\textsuperscript{3}\\
\textsuperscript{1}School of Informatics, University of Edinburgh\\
\textsuperscript{2}Institute of Formal and Applied Linguistics, Charles University in Prague\\
\textsuperscript{3}School of Computer Science and Engineering, Hebrew University of Jerusalem\\
\texttt{a.birch@ed.ac.uk, bhaddow@inf.ed.ac.uk}\\
\texttt{bojar@ufal.mff.cuni.cz, oabend@cs.huji.ac.il}\\
}

@@

Human evaluation of machine translation normally uses sentence-level measures such as relative ranking or adequacy scales. However, these provide no insight into possible errors,
and do not scale well with sentence length.
We argue for a semantics-based evaluation, which captures what meaning components
are retained in the MT output, providing a more fine-grained analysis of
translation quality, and enables the construction and tuning of semantics-based MT. 
We present a novel human semantic evaluation measure, Human
UCCA-based MT Evaluation (HUME), building on the UCCA semantic representation scheme.
%Making progress over previous work, the proposed measure takes into account
HUME covers
a wider range of semantic phenomena than previous methods and does not rely on semantic annotation
of the potentially garbled MT output. 
%itself, whose interpretation is often unclear.
We experiment with four language pairs, demonstrating HUME's broad applicability,
and report good
%as well as its reliability, reflected in its 
inter-annotator agreement rates and 
 correlation with human adequacy scores.
